---
title: "Weight of Fish"
author: "Sylvia Rodriguez"
date: "Year 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```


```{r}
Fish=read.csv("Fish.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

In this assignment, we are showing the weight of fish using different numerical tables and graphs. We are trying to find the best two variables to predict the weight of each type of fish. 

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Subset of the fish I want to analyze. Then I will look at how well each combination of the predictor variables can predict the weight of the fish. We are using the perch subset in my analysis. 


```{r}
perch=filter(Fish,Species=="Perch")
```

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicNN <- ggplot(perch,aes(y=Weight,x=Length1^2))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```
  
  
###get fancy  


```{r}
basicNN + geom_point() + geom_smooth(method=lm) 
```
  

These line plots are pretty standard. It shows that the longer length of the fish, the heavier they weight. There are many more fish that are smaller and lighter than bigger and heavier. 


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Fish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
The graph shows that the Y axis is adjusted R square, and the X axis is the number of variables used in a linear fit.



```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

The summary shows which two variables are best, which is height and width. 


```{r}
best.model <- lm(Weight~Height+Width,data=perch)
summary(best.model)
fullup=lm(Weight~ .,data= select(perch, -Species))
```


We made a linear model based on height and width. It shows that the best prediction for weight = -536 + 74.77 * Height +69.62 * width.

This equation is the best fit for predicting the weight of the perch using the two variables, width and height. 


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


$H_0$: there is no difference between models 1 and 2 when predicting the weight of the fish (perch)

$H_A$: there is no difference between models 1 and 2 when predicting the weight of the fish

```{r}
anova(fullup,best.model)
```

This analysis of variance table basically shows that model 1 is slightly better because it has a smaller residual sum of squares. 


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


We fail to reject the null hypothesis because the P value is high at 0.879. We conclude that Height and Width are the two best varaible when predicting weight. 